\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-23 paper.tex
added related work subsection on DSLs

@@

IDS in WSN \cite{perrig2004security,mishra2004intrusion}

DSL \cite{fowler2010domain,mernik2005and}

DSL for WSN \cite{naumowicz2009prototyping,levis2004tinyscript}

DSL for IDS \cite{sekar1999high} \cite{uppuluri2001experiences} \cite{eckmann2002statl} \cite{vigna2003designing}

>>>>

\usepackage[autostyle]{csquotes}

@@

Section \ref{classification} introduced some ID
algorithms\cite{ganeriwal2008reputation,mishra2004intrusion,krontiris2009cooperative}
and presented a classification\cite{mishra2004intrusion,ioannis2007towards,alrajeh2013intrusion}
based on their detection approach and interaction style.

This section now focuses on related work in the field of domain specific
languages and code generation, both in relation to wireless networks of
resource constraint devices. These two components are the core of the \NAME
framework and the solution it proposes. We also look at the more general scope,
how these concepts are applied in other disciplines and evaluate their
relevance in the scope of intrusion detection in the IoT and the proposed \NAME
framework.

\subsection{Domain Specific Languages}

Using a DSL, and especially an external DSL, as a foundation for any solution
requires special care. It's important to remember that a DSL is merely a
\emph{thin veneer over a (semantic) model}\cite{fowler2010domain}. Its sole
purpose should be the easing of filling out the model. In the case of \NAME the
reasons to implement a DSL are valid: the key goal is to remove any technical
restrictions from a formal description of ID algorithms, allowing domain
experts to produce these specifications\cite{mernik2005and}.

Zooming in on wireless networks of resource constraint devices, we see that
DSLs are indeed introduced \enquote{to shorten the development cycles
dramatically during deployments, to reduce the dependency on hardware and
software engineers, and to lead to a wider adoption outside the computer
science field}\cite{sadilek2008domain,naumowicz2009prototyping}.

TinyScript\cite{levis2004tinyscript} is an example of a language for wireless
sensor networks. It's a complete programing language that aims to ease the
description of algorithms in general. The Basic-like syntax does enable more
productive development. But this approach doesn't address the underlying
resource problems inherently connected to the context.

SEAL\cite{elsts2013seal} is a novel complete programming language that focuses
on novice programmers. It is a clear fit for \emph{sense-and-send} type of
applications, and doesn't pretend to be the best choice for any type of
application. It does however share the idea of event to overcome the technical
nature of loops.

Shifting the scope to intrusion detection, we learn that DSLs are predominantly
used to describe patterns of events found in network
packets\cite{sekar1999high,roesch1999snort} in a concise way.

BMSL\cite{uppuluri2001experiences} is a DSL that allows the specification of
patterns and actions. Patterns can contain events extracted from log files,
system calls and network packets.

The STAT framework with its STATL
language\cite{eckmann2002statl,vigna2003designing} are not intrusion detection
specific, but through extensions they allow to model attack scenarios using
state machines. This is an interesting approach that shares the same ideas as
our event-driven concept. The framework generates C++.

\subsection{Code Generation}

Code generation can be applied for a number reasons. In combination with a DSL
it can optimize a development process, reducing the amount of code that needs
to be constructed or it can be used to systematically create better code.

Embedded systems are a prime example of an environment where code needs to be
of a high quality.
